\documentclass[11pt]{article}
\usepackage[margin=0.8in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\lhead{\textbf{Chloe Mathews}}
\rhead{\href{mailto:chloe@chloemathews.net}{chloe@chloemathews.net} \enspace $\mid$ \enspace \href{https://github.com/cmathews393}{https://github.com/cmathews393}}
\renewcommand{\headrulewidth}{0.4pt}
\begin{document}
\begin{center}
  {\LARGE \textbf{Chloe Mathews}}\\[4pt]
  Boise, Idaho/Minneapolis, MN (Spring 2026) \\
  \href{mailto:chloe@chloemathews.net}{chloe@chloemathews.net} \quad \href{https://github.com/cmathews393}{https://github.com/cmathews393}
\end{center}
\vspace{8pt}

\section*{Summary}
I help organizations solve issues with automation and process improvement. I am passionate about modernizing legacy processes using automation. I have a strong desire to make people's lives better
with automation and integrations, speeding up work and making people more efficient.


\section*{Work Experience}

\noindent\textbf{DevOps Engineer} \hfill \small{Nov 2021 -- Present}\\
\textit{Endsight}\\

\begin{itemize}[leftmargin=*]
  
    \item Spearheaded large scale project aimed at reducing alert noise for NOC Engineers, using Streamlit and Python to visualize and slice data for trend analysis
  
    \item Utilized multiple (4+) vendor APIs and FastAPI/Streamlit to create and track projects, merging data across disparate systems for a unified overview.
  
    \item Fostered an environment of collaboration by working with other internal teams, vendors, and fellow teammembers to establish goals and improve team capability.
  
\end{itemize}

\vspace{6pt}

\noindent\textbf{NOC Engineer} \hfill \small{Jan 2020 -- Nov 2021}\\
\textit{Flextechs}\\

\begin{itemize}[leftmargin=*]
  
    \item Worked with clients to improve monitoring of backups and internal systems
  
    \item Led an effort to improve framework compliance (HIPAA, PCI) and internal system security
  
    \item Led recovery efforts after security incidents, including ransomware attacks.
  
\end{itemize}

\vspace{6pt}

\noindent\textbf{Ops Technician} \hfill \small{Jun 2019 -- Jan 2020}\\
\textit{IP Services}\\

\begin{itemize}[leftmargin=*]
  
    \item Improved skill with networking technologies (Solarwinds, Fortigate, Juniper, Cisco)
  
    \item Assisted in the deployment and management of network infrastructure in a small colocation environment with around 15 clients.
  
    \item Assisted with troubleshooting client issues.
  
\end{itemize}

\vspace{6pt}


\section*{Education}

\noindent\textbf{Lane Community College} \hfill \small{2018 -- 2019}\\
\small{AAS \textbullet\ Computer Network Operations \textbullet\ Graduated 2019} 
\vspace{6pt}


\section*{Skills}
\begin{tabular}{@{}p{0.25\textwidth}@{}p{0.7\textwidth}@{}}

\textbf{Frontend} & React, TypeScript \\

\textbf{Backend} & Python, Node.js, Rust, PHP \\

\textbf{Mobile} & Flutter \\

\textbf{DevOps} & Ansible \\

\textbf{Obs/Mon} & Honeycomb, OpenTelemetry, Grafana \\

\textbf{CI/CD} & GitHub Actions \\

\textbf{Cloud} & Vercel, Azure, Cloudflare \\

\textbf{Databases} & PostgreSQL, SQLite, Microsoft SQL Server \\

\end{tabular}

\section*{Achievements}

\begin{itemize}[leftmargin=*]
  
    \item 100k lines of code authored in private work repositories, \textasciitilde{}10k+ lines in open source projects
  
\end{itemize}


\end{document}
